\chapter{Issues \& TODOs}
\label{overview}

  \section{Issues}
    \begin{enumerate}[label=(\roman*)]
      \item During installation, CisDsc.ps1 copies backup DSC modules from \textbackslash\textbackslash files, rather than using the standard installation method. This is because the command \verb|Install-Module| does not work in CIS network. The error is \say{Unable to download from URI\\ \say{\url{https://go.microsoft.com/fwlink/?LinkID=627338\&clcid=0x4}}}. The Network Team was not able to identify the problem. It is very likely that GPO blocks the connection.
      \item Credential encryption is not implemented. To justify the use of domain user account, note that DSC Local Configuration Manager by default runs as SYSTEM. It does not have access to SMB share files unless we provide it with domain credentials. This is necessary for \verb|[File]BGInfo|.\\
      \textbf{Were this project to be continued, this should be top priority.} For instructions, visit \url{https://blogs.msdn.microsoft.com/powershell/2014/01/31/want-to-secure-credentials-in-windows-powershell-desired-state-configuration/}.
      \item HTTPS is not implemented. This can be easily configured once you have a certificate, but it could complicate the logic in \verb|Install-CisDscPullServer|. The best practice would be to configure manually, after the pull server is installed.
    \end{enumerate}

  \section{TODOs}
    \begin{enumerate}[label=(\roman*)]
      \item Once credential encryption issue is resolved, uncomment the following lines in \verb|[File]BGInfo|.\\
      \verb^#SourcePath = "\\files\dfs\CISWindows\Software\DSCBackup\BGInfo32-64"^\\
      \verb^#MatchSource = $true^\\
      \verb^#Recurse = $true^\\
      \verb^#Credential = $Credential^\\
      \item Change current implementation of WMF 5 check. Rather than attempting to install it remotely, which always fails, maybe notify a systems administrator.
      \item Find out why \verb|[Script]DEP| in the template does not work on Server 2012 machines.
      \item Add IISCrypto settings in template.
    \end{enumerate}